---
title: "Calculations notebook"
author: Benjamin Banks
date: October 26, 2023,
output:
    pdf_document: default
---

## Pre calculations

In the pre trail we have 20 total obs.
Load the pre data:

```{r warning=FALSE}
library(readxl)
preData <- read_excel("C:/Users/Benja/dev/dtu/Image-segmentation/data/data.xlsx",
    sheet = "Initial", col_types = "numeric")
```

The means of them:

```{r}
mean(preData$Accuraccy)
```

And the standard deviation

```{r}
sd(preData$Accuraccy)
```

We will use the above information in a power analysis, to calcualte how many observations our final experiment requires.

```{r}
power.t.test(power=0.8, delta = 0.05, sd = 0.2159476, sig.level = 0.05)
```

So the we will make 300 observations pr. model.

## Final calculations

Load the final data:

```{r warning=FALSE}
library(readxl)
finalData <- read_excel("C:/Users/Benja/dev/dtu/Image-segmentation/data/data.xlsx",
    sheet = "Final", col_types = "numeric")
```

Find the mean:

```{r}
colMeans(finalData)
```

T-test with initial_k_means_iterations = 1 and initial_k_means_iterations = 2

```{r}
t.test(finalData$init_k_means_1, finalData$init_k_means_2)
```
